### 2023-01-22 appendix_kronecker/appendix.tex
post-reviews, pre supervisor feedback

Let \(\bs H_{12}(t)\) be the top-right quadrant of \(e^{\bs Bt}\) of size \(m_1\times m_2\), i.e.
\begin{align}
	\bs H_{12}(t) &= \vligne{  \bs I_{m_1\times m_1} & \bs 0}e^{\bs Bt} \left[\begin{array}{c} \bs 0 \\ \bs I_{m_2\times m_2}\end{array}\right]. \label{eqn: p03j}
\end{align}
Denote by \(\widehat{\bs H}_{11}(\lambda):=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{11}(t)\wrt t\) and by \(\widehat{\bs H}_{12}(\lambda):=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{12}(t)\wrt t\), the Laplace transforms of \(\bs H_{11}(t)\) and \(\bs H_{12}(t)\), respectively. Using Lemma~\ref{lem: sfkjgn} we can show the following result. 
\begin{lem} Assuming \(\lambda >0\) and \(\lambda\bs I-\bs B_{22}\) is invertible, then 
	\begin{align}
		\widehat{\bs H}_{11}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \wrt x,\label{eqn: 202}
		%
		\\\widehat{\bs H}_{12}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\wrt x.\label{eqn: 203}
	\end{align}
\end{lem}
\begin{proof}
	First we show the result for \(\widehat{\bs H}_{11}(\lambda)\). Taking the Laplace transform of (\ref{eqn: akg987LKJ}) shows that \(\widehat{\bs H}_{11}(\lambda)\) is equal to 
	\begin{align}
		&\int_{t=0}^\infty \int_{v=0}^t\int_{u=v}^t e^{-\lambda (t-u)}e^{\bs B_{11}(t-u)}\bs B_{12}e^{-\lambda (u-v)}e^{\bs B_{22}(u-v)}\bs B_{21}e^{-\lambda v}\bs H_{11}(v)\wrt u\wrt v \nonumber 
		\\&\qquad{}+ (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\nonumber 
		%
		\\& = (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1} + (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\widehat{\bs H}_{11}(\lambda),
	\end{align}
	by the convolution theorem for Laplace transforms. This implies
	\begin{align*}
		&\left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]\widehat{\bs H}_{11}(\lambda) 
		\\&= (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1},
	\end{align*}
	and therefore 
	\begin{align*}
		&\widehat{\bs H}_{11}(\lambda) 
		\\&= \left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1} (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}
		%
		\\&= \left[(\lambda \bs I_{m_1\times m_1} - \bs B_{11})\left(\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)\right]^{-1} 
		%
		\\&= \left[\lambda \bs I_{m_1\times m_1} - \bs B_{11} - \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1}
		%
		\\&= \int_{t=0}^\infty e^{\left(\bs B_{11} - \lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)t}\wrt t,
	\end{align*}
	which is (\ref{eqn: 202}).

>>>>

Let \(\bs H_{12}(t)\) be the top-right quadrant of \(e^{\bs Bt}\) of size \(m_1\times m_2\), i.e.
\begin{align}
	\bs H_{12}(t) &= \vligne{  \bs I_{m_1\times m_1} & \bs 0}e^{\bs Bt} \left[\begin{array}{c} \bs 0 \\ \bs I_{m_2\times m_2}\end{array}\right]. \label{eqn: p03j}
\end{align}
Denote by \(\widehat{\bs H}_{11}(\lambda)=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{11}(t)\wrt t\) and by \(\widehat{\bs H}_{12}(\lambda)=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{12}(t)\wrt t\), the Laplace transforms of \(\bs H_{11}(t)\) and \(\bs H_{12}(t)\), respectively. Using Lemma~\ref{lem: sfkjgn} we can show the following result. 
\begin{lem} Assuming \(\lambda >0\) and \(\lambda\bs I-\bs B_{22}\) is invertible, then 
	\begin{align}
		\widehat{\bs H}_{11}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \wrt x,\label{eqn: 202}
		%
		\\\widehat{\bs H}_{12}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\wrt x.\label{eqn: 203}
	\end{align}
\end{lem}
\begin{proof}
	First we show the result for \(\widehat{\bs H}_{11}(\lambda)\). Taking the Laplace transform of (\ref{eqn: akg987LKJ}) shows that \(\widehat{\bs H}_{11}(\lambda)\) is equal to 
	\begin{align}
		&\int_{t=0}^\infty \int_{v=0}^t\int_{u=v}^t e^{-\lambda (t-u)}e^{\bs B_{11}(t-u)}\bs B_{12}e^{-\lambda (u-v)}e^{\bs B_{22}(u-v)}\bs B_{21}e^{-\lambda v}\bs H_{11}(v)\wrt u\wrt v \nonumber 
		\\&\qquad{}+ (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\nonumber 
		%
		\\& = (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1} + (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\widehat{\bs H}_{11}(\lambda),
	\end{align}
	by the convolution theorem for Laplace transforms. This implies
	\begin{align*}
		&\left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]\widehat{\bs H}_{11}(\lambda) 
		\\&= (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1},
	\end{align*}
	and therefore 
	\begin{align*}
		&\widehat{\bs H}_{11}(\lambda) 
		\\&= \left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1} (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}
		%
		\\&= \left[(\lambda \bs I_{m_1\times m_1} - \bs B_{11})\left(\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)\right]^{-1} 
		%
		\\&= \left[\lambda \bs I_{m_1\times m_1} - \bs B_{11} - \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1}
		%
		\\&= \int_{t=0}^\infty e^{\left(\bs B_{11} - \lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)t}\wrt t,
	\end{align*}
	which is (\ref{eqn: 202}).
